---
title: "Advanced Marketing Analytics Projects in R"
author: "Khyati Chauhan"
output: html_document
---

# 🎬 Project 1: Multi-Touch Attribution (Markov Model)

This project simulates multi-channel user journeys and applies attribution models
to understand which marketing channels contribute most to conversions.

```{r}
# Install if needed: install.packages("ChannelAttribution"); install.packages("reshape2")
library(ChannelAttribution)
library(reshape2)

# Simulated user journey data
set.seed(42)
df <- data.frame(
  path = c("Google > YouTube > Direct",
           "Facebook > Direct",
           "Email > Google > Direct",
           "YouTube > Direct",
           "Organic > Email > Direct",
           "Google > Facebook > Direct",
           "Email > Direct",
           "App > Direct",
           "YouTube > Email > Direct",
           "Google > Organic > Direct"),
  conv = sample(50:200, 10),
  null = 0
)

# Apply Markov Attribution Model
markov_model <- markov_model(df, var_path="path", var_conv="conv", var_null="null", order=1)
print(markov_model)
```

---

# 🎯 Project 2: Conversion Funnel + Predictive Modeling

This project builds a predictive model to estimate purchase probability from funnel data.

```{r}
# Install if needed: install.packages("caret"); install.packages("pROC"); install.packages("randomForest")
library(caret)
library(pROC)
library(randomForest)

# Simulated funnel data with user features
set.seed(42)
funnel <- data.frame(
  age = sample(18:60, 500, replace=TRUE),
  sessions = rpois(500, 5),
  region = sample(c("US","EU","APAC"), 500, replace=TRUE),
  signup = rbinom(500, 1, 0.6),
  add_to_cart = rbinom(500, 1, 0.4),
  purchase = rbinom(500, 1, 0.3)
)

# Train/Test split
trainIndex <- createDataPartition(funnel$purchase, p = .7, list = FALSE)
train <- funnel[trainIndex,]
test  <- funnel[-trainIndex,]

# Random Forest model
model <- randomForest(as.factor(purchase) ~ age + sessions + region + signup + add_to_cart, data=train)
pred <- predict(model, test, type="prob")[,2]

# ROC Curve
roc_curve <- roc(test$purchase, pred)
plot(roc_curve, col="blue")
auc(roc_curve)
```

---

# 🧪 Project 3: Bayesian A/B Testing

This project demonstrates Bayesian A/B testing to evaluate if a new variant outperforms the old one.

```{r}
# Bayesian A/B Test (without bayesAB)
set.seed(42)

# Data: conversions
A <- rbinom(500, 1, 0.12)
B <- rbinom(500, 1, 0.16)

# Priors: Beta(1,1) uniform
alpha_prior <- 1
beta_prior <- 1

# Posterior distributions
posterior_A <- rbeta(10000, sum(A) + alpha_prior, length(A) - sum(A) + beta_prior)
posterior_B <- rbeta(10000, sum(B) + alpha_prior, length(B) - sum(B) + beta_prior)

# Probability that B > A
prob_B_better <- mean(posterior_B > posterior_A)

hist(posterior_A, col=rgb(1,0,0,0.5), xlim=c(0,0.3), main="Posterior Distributions", xlab="Conversion Rate")
hist(posterior_B, col=rgb(0,0,1,0.5), add=TRUE)
legend("topright", c("A","B"), fill=c(rgb(1,0,0,0.5), rgb(0,0,1,0.5)))

cat("Probability that B is better than A:", prob_B_better, "\\n")


```

---

# ✅ Conclusion

- **Markov Model Attribution** reveals hidden influential channels beyond last-click.  
- **Predictive Modeling** helps identify which users are most likely to convert.  
- **Bayesian A/B Testing** provides more intuitive probability-based insights than p-values.  

These projects demonstrate advanced marketing analytics capabilities combining **R, statistics, and machine learning**.
